A 3d curvilinear skeletonization algorithm with application to bidirectional path tracing

### 2012-09-10 bidir_pathtrace_skeleton.tex

\title{A 3d curvilinear skeletonization algorithm with application to bidirectional path tracing}
\author{John Chaussard \and Venceslas Biri \and Michel Couprie}
\institute{Universit\'{e} Paris Est, LABINFO-IGM, A2SI-ESIEE \\ 2, boulevard Blaise Pascal, Cit\'{e} DESCARTES \\ BP 99  93162 Noisy le Grand CEDEX, France \\ \email{chaussaj@esiee.fr, bertrang@esiee.fr, coupriem@esiee.fr}}

>>>>

\title{A 3d curvilinear skeletonization algorithm with application to bidirectional path tracing}
\author{John Chaussard\inst{1} \and Laurent No\"{e}l\inst{2} \and Venceslas Biri\inst{2} \and Michel Couprie\inst{2}}
\institute{Universit\'{e} Paris 13, Sorbonne Paris Cit\'{e}, LAGA, CNRS(UMR 7539), \\ F-93430, Villetaneuse, France \\ \email{chaussard@math.univ-paris13.fr}
\and
Universit\'{e} Paris Est, LABINFO-IGM, A3SI-ESIEE \\ 2, boulevard Blaise Pascal, Cit\'{e} DESCARTES \\ BP 99  93162 Noisy le Grand CEDEX, France \\ \email{laurent.noel@esiee.fr, v.biri@esiee.fr, michel.couprie@esiee.fr}}
